\section{Full Risk Register}
\label{app:risk-register}
\label{sec:risk-register}

Supports DPIA item~7 and steering-committee review.
Residual risks require explicit acceptance by leadership and DPO.

\begin{longtable}{@{}p{0.9cm}p{3.0cm}p{1.8cm}p{1.6cm}p{4.6cm}@{}}
\toprule
ID & Risk & Impact & Level & Mitigation \\
\midrule
\endhead
R1 & Misinterpretation as surveillance & Trust loss & High &
  Transparency; no biometrics; signage; training. \\
R2 & False positive alerts & Alert fatigue & Med &
  Calibration; human review; tabletop tuning. \\
R3 & False negative (missed stress) & Safety gap & Med &
  Multimodal fusion; manual protocol backstop. \\
R4 & Raw media retention failure & Privacy breach & High &
  TTL enforcement; storage audits; forbidden egress. \\
R5 & Unauthorized dashboard access & Exposure & Med &
  RBAC, MFA, SSO, audit logging. \\
R6 & Integrator adds facial recognition & Scope creep & High &
  Architecture review; contract clauses; acceptance tests. \\
R7 & Autonomous actuation wired & Governance violation & High &
  No actuation APIs; SOP; technical inspection. \\
R8 & Coordination service outage & Awareness loss & Med &
  Degraded mode SOP; UPS; monitoring. \\
R9 & Hardware supply / thermal delay & Schedule & Low &
  CPU fallback; vendor SLA. \\
R10 & Children's data sensitivity & Regulatory scrutiny & High &
  DPIA; DPO oversight; minimization. \\
R11 & Cross-border transfer & Legal risk & Med &
  On-prem default; DPAs; transfer assessment. \\
R12 & Misleading advisory explanations & Staff confusion & Med &
  Grounding checks; mandatory review; UI disclaimers. \\
R13 & Consortium scope drift & Governance conflict & Med &
  Consortium charter; change control. \\
R14 & Insufficient training & Misuse & Med &
  Mandatory training gates before go-live. \\
R15 & Community opposition & Pilot halt & Med &
  Co-design; early ethics consultation; opt-out. \\
\bottomrule
\end{longtable}

Review monthly and after any incident.
Escalate High residual risks before phase transitions.
