\section{Reference Hardware Bill of Materials}
\label{app:hardware-bom}
\label{sec:hardware-procurement-bom}

This appendix provides an \textbf{indicative Bill of Materials (BOM)} for school pilot budgeting,
Horizon Europe equipment planning, and IT procurement discussions.
It is \textbf{not} a final purchase order, tender specification, or conformity statement.

\smallskip
\noindent\fbox{\parbox{0.97\textwidth}{\small
\textbf{Disclaimer.}
Prices are approximate EUR ranges and vary by country, taxes, availability, procurement framework,
educational discounts, and vendor agreements.
Final purchasing decisions require institutional IT and procurement validation.
This BOM does \textbf{not} certify GDPR, EU AI Act, or operational safety effectiveness.
All tiers assume \textbf{advisory-only} operation, \textbf{no default raw media retention}, and
exclusions in Box~\ref{box:system-boundaries} (no facial recognition, biometrics, or autonomous actuation).
}}

\subsection{Tier overview}

\begin{table}[htbp]
  \centering
  \caption{Deployment tier scope (Appendix~E).}
  \label{tab:bom-tier-overview}
  \small
  \begin{tabular}{@{}p{2.2cm}p{2.0cm}p{2.0cm}p{5.8cm}@{}}
    \toprule
    Tier & Schools & Zones & Purpose \\
    \midrule
    A --- Minimal & 1 & 2--6 &
      Sandbox, tabletops, limited MVP; low-cost feasibility. \\
    B --- Horizon & 1--3 & 10--20 &
      Multimodal pilots; operator workflow and governance evaluation. \\
    C --- Multi-site & 5--10 & 10--20 / site &
      Federation-ready; redundancy; audit and backup maturity. \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Tier A --- Minimal Pilot}

\textbf{Scope:} one school; two to six sensing zones; sandbox and mandatory tabletops before limited
MVP live sensing.
\textbf{Expected total (CapEx, indicative):} approximately EUR~8{,}000--20{,}000 depending on reuse
of existing cameras, cabling plant, and integrator services.

\begin{longtable}{@{}p{0.7cm}p{2.4cm}p{2.6cm}r r p{2.2cm}p{2.5cm}@{}}
  \caption{Tier A --- reference BOM (indicative).}
  \label{tab:bom-tier-a} \\
  \toprule
  Cat. & Model / reference & Qty & Unit & Subtotal & Role & Notes / alternatives \\
  \midrule
  \endfirsthead
  \multicolumn{7}{l}{\textit{Tier A BOM (continued)}} \\
  \toprule
  Cat. & Model / reference & Qty & Unit & Subtotal & Role & Notes / alternatives \\
  \midrule
  \endhead
  \midrule
  \multicolumn{7}{r}{\textit{Continued on next page}} \\
  \endfoot
  \bottomrule
  \endlastfoot
  A & Seeed reComputer J4012 (Jetson Orin Nano 8GB) & 2 & 650 & 1{,}300 &
    Zone edge compute & Alt:\ Orin Nano Dev Kit + carrier \\
  A & Intel NUC 13 Pro / ASUS NUC i5 & 1 & 750 & 750 &
    Light zone / sandbox & Alt:\ fanless i7 mini-PC \\
  B & Reolink RLC-810A PoE (ONVIF) & 4 & 95 & 380 &
    Zone video & Reuse approved existing PoE cameras \\
  B & --- (existing ONVIF) & 0 & --- & 0 &
    Optional reuse & DPIA scope review required \\
  C & USB boundary microphone (sandbox) & 2 & 60 & 120 &
    Tabletop / lab audio & No speaker ID; no STT by default \\
  C & Ambient SPL sensor (local USB) & 1 & 90 & 90 &
    Optional zone level & No voiceprint analytics \\
  D & Door contact sensor (wired) & 2 & 25 & 50 &
    Exit / door state & Optional; BMS feed if approved \\
  D & CO\textsubscript{2} / temp sensor (IoT) & 1 & 80 & 80 &
    Environmental context & Structured feed only \\
  E & MikroTik CRS112-8P-4S-IN PoE & 1 & 220 & 220 &
    PoE + VLAN & Alt:\ TP-Link Omada 8-port PoE \\
  F & MikroTik RB5009UG+S+IN & 1 & 180 & 180 &
    Router / firewall & Alt:\ existing school FW \\
  G & Intel NUC 13 Pro (orchestrator) & 1 & 750 & 750 &
    Site coordination & Event queue + audit \\
  H & Synology DS723+ + 2×4TB IronWolf & 1 & 650 & 650 &
    Logs / config backup & Not raw video archive \\
  I & APC Smart-UPS 750VA (SMC750I) & 2 & 180 & 360 &
    Edge + orchestrator & 15--20 min autonomy target \\
  J & ASUS NUC / mgmt laptop & 1 & 650 & 650 &
    IT provisioning & MFA / SSO preferred \\
  K & 6U lockable wall cabinet & 1 & 280 & 280 &
    Physical security & Cable mgmt + asset tags \\
  L & --- & 0 & --- & 0 &
    Federation & Disabled in Tier A \\
  M & External USB backup disk & 1 & 120 & 120 &
    Offline backup & Rotated offsite \\
  \midrule
  \multicolumn{5}{r}{\textbf{Indicative hardware subtotal}} &
    \multicolumn{2}{r}{\textbf{$\approx$6{,}000--7{,}000}} \\
\end{longtable}

\noindent Add installation, cabling, spares, and VAT to reach EUR~8{,}000--20{,}000 total CapEx range.

\subsection{Tier B --- Horizon Pilot}

\textbf{Scope:} one to three schools; ten to twenty sensing zones per lead site; multimodal
experimentation and operator workflow evaluation under governance gates.
\textbf{Expected total (CapEx, indicative):} approximately EUR~25{,}000--90{,}000 depending on zone
count, GPU tier, number of schools, and integration depth.

\begin{longtable}{@{}p{0.7cm}p{2.4cm}p{2.6cm}r r p{2.2cm}p{2.5cm}@{}}
  \caption{Tier B --- reference BOM per lead site (indicative).}
  \label{tab:bom-tier-b} \\
  \toprule
  Cat. & Model / reference & Qty & Unit & Subtotal & Role & Notes / alternatives \\
  \midrule
  \endfirsthead
  \multicolumn{7}{l}{\textit{Tier B BOM (continued)}} \\
  \toprule
  Cat. & Model / reference & Qty & Unit & Subtotal & Role & Notes / alternatives \\
  \midrule
  \endhead
  \midrule
  \multicolumn{7}{r}{\textit{Continued on next page}} \\
  \endfoot
  \bottomrule
  \endlastfoot
  A & Seeed reComputer J4011 (Orin NX 16GB) & 4 & 1{,}100 & 4{,}400 &
    Zone edge (heavy) & Alt:\ Orin NX module + industrial carrier \\
  A & Seeed reComputer J4012 (Orin Nano 8GB) & 2 & 650 & 1{,}300 &
    Light zones & Proportional GPU buy \\
  A & Jetson AGX Orin 32GB (J4021) & 1 & 2{,}400 & 2{,}400 &
    Optional fusion headroom & If $>$15 zones \\
  B & Reolink RLC-810A / 820A PoE & 12 & 110 & 1{,}320 &
    Zone video & Avoid cloud-only cameras \\
  B & Axis M1065-L / M31 (alt.) & 2 & 350 & 700 &
    Higher-governance alt. & Where existing Axis VMS \\
  C & PoE ambient audio / SPL sensor & 4 & 150 & 600 &
    Zone acoustic level & \textbf{No} speaker ID / voiceprint \\
  C & ReSpeaker USB 4-Mic (sandbox) & 2 & 75 & 150 &
    Training / tabletop & Not for covert monitoring \\
  D & Door contact + occupancy counter & 4 & 45 & 180 &
    Access / flow context & BMS integration if approved \\
  D & Environmental (CO\textsubscript{2}, temp) & 3 & 80 & 240 &
    Zone context & No profiling \\
  E & MikroTik CRS328-24P-4S+RM PoE & 1 & 380 & 380 &
    Core PoE switch & Alt:\ UniFi USW-24-PoE \\
  E & Cat6 patch panel + cabling (est.) & 1 & 400 & 400 &
    Plant & Site survey required \\
  F & Ubiquiti Dream Machine Pro & 1 & 380 & 380 &
    FW / VLAN / VPN & Alt:\ RB5009, pfSense appliance \\
  G & Seeed J4021 AGX Orin / fanless i7+GPU & 1 & 2{,}400 & 2{,}400 &
    Local orchestrator & HA optional (2nd NUC) \\
  H & Synology DS923+ + 4×4TB WD Red Plus & 1 & 1{,}350 & 1{,}350 &
    Audit + backup & Structured events only \\
  I & APC Smart-UPS 1000VA (SMT1000I) & 2 & 420 & 840 &
    Rack / orchestrator & Eaton 5P equivalent \\
  I & APC Smart-UPS 750VA (edge) & 2 & 180 & 360 &
    Remote edge nodes & \\
  J & Intel NUC 13 Pro + safety laptop & 2 & 900 & 1{,}800 &
    IT + dashboard access & SSO / MFA \\
  K & 9U lockable wall cabinet + PDU & 1 & 450 & 450 &
    Comms closet & Tamper-evident labels \\
  L & Intel NUC federation node & 1 & 750 & 750 &
    Research export (opt.) & Anonymized metrics; off by default \\
  M & Rotating USB + NAS snapshot & 1 & 250 & 250 &
    Backup media & Immutable copy policy \\
  \midrule
  \multicolumn{5}{r}{\textbf{Indicative per-site hardware subtotal}} &
    \multicolumn{2}{r}{\textbf{$\approx$20{,}000--22{,}000}} \\
\end{longtable}

\noindent Multi-school Tier~B (2--3 sites): multiply per-site BOM; add EUR~5{,}000--15{,}000 integration
and harmonization per replica site.
Upper bound EUR~90{,}000 includes full greenfield plant and professional installation.

\subsection{Tier C --- Multi-site / Production Candidate}

\textbf{Scope:} five to ten schools; federation-ready architecture; resilient infrastructure and
stronger audit, backup, and governance controls.
\textbf{Expected total (CapEx, indicative):} approximately EUR~100{,}000--350{,}000 depending on
school count, redundancy, federation hub, and integrator scope.

\begin{longtable}{@{}p{0.7cm}p{2.4cm}p{2.6cm}r r p{2.2cm}p{2.5cm}@{}}
  \caption{Tier C --- reference BOM per site (indicative).}
  \label{tab:bom-tier-c} \\
  \toprule
  Cat. & Model / reference & Qty & Unit & Subtotal & Role & Notes / alternatives \\
  \midrule
  \endfirsthead
  \multicolumn{7}{l}{\textit{Tier C BOM (continued)}} \\
  \toprule
  Cat. & Model / reference & Qty & Unit & Subtotal & Role & Notes / alternatives \\
  \midrule
  \endhead
  \midrule
  \multicolumn{7}{r}{\textit{Continued on next page}} \\
  \endfoot
  \bottomrule
  \endlastfoot
  A & Seeed reComputer J4011 (Orin NX 16GB) & 6 & 1{,}100 & 6{,}600 &
    Zone edge & Spare unit recommended \\
  A & Jetson AGX Orin Dev Kit / J4021 & 2 & 2{,}400 & 4{,}800 &
    Orchestrator HA pair & Active/passive or load-split \\
  A & Fanless industrial i7 + NVIDIA T400 & 1 & 1{,}800 & 1{,}800 &
    Alt.\ orchestrator & Vendor-neutral option \\
  B & Reolink / Axis M-series PoE & 16 & 120 & 1{,}920 &
    Standardized zone video & ONVIF; no cloud lock-in \\
  C & PoE ambient SPL / acoustic sensor & 8 & 150 & 1{,}200 &
    Multimodal zones & No STT / voiceprint \\
  D & Door, occupancy, environmental kit & 8 & 50 & 400 &
    Structured sensor feeds & BMS/legal approval \\
  E & MikroTik CRS326-24G-2S+RM + CRS328 PoE & 2 & 400 & 800 &
    Core + edge switching & Redundant uplinks \\
  F & Netgate pfSense / RB5009 + VPN & 2 & 450 & 900 &
    FW HA / segmentation & School SOC integration \\
  G & AGX Orin pair + rack orchestrator & 2 & 2{,}400 & 4{,}800 &
    Local orchestration & Degraded-mode tested \\
  H & Synology RS822+ + 4×8TB IronWolf & 1 & 2{,}800 & 2{,}800 &
    Audit tier storage & Encryption at rest \\
  I & APC Smart-UPS 1500VA + Eaton 5P & 2 & 550 & 1{,}100 &
    Rack power & Graceful shutdown scripts \\
  J & Managed admin laptop + NUC jump host & 3 & 900 & 2{,}700 &
    IT / DPO / safety & MFA mandatory \\
  K & 12U lockable rack + PDU + labeling & 1 & 850 & 850 &
    Physical security & Asset inventory \\
  L & Dell PowerEdge T350 / on-prem VM host & 1 & 3{,}500 & 3{,}500 &
    Federation hub (opt.) & Cloud-disabled; aggregates only \\
  M & Offline immutable backup rotation & 1 & 500 & 500 &
    DR readiness & 3-2-1 backup rule \\
  \midrule
  \multicolumn{5}{r}{\textbf{Indicative per-site hardware subtotal}} &
    \multicolumn{2}{r}{\textbf{$\approx$35{,}000--38{,}000}} \\
\end{longtable}

\noindent\textbf{Consortium layer (once):} federation / research server EUR~3{,}500--8{,}000;
multi-site integration EUR~15{,}000--40{,}000.
Five sites at mid-tier $\approx$ EUR~190{,}000--250{,}000; upper bound EUR~350{,}000 with full
redundancy and professional integration across ten sites.

\subsection{Hardware selection rationale}

\textbf{Local-first processing.}
Jetson Orin and equivalent fanless hosts run perception and semantic abstraction on school premises.
Structured zone summaries---not raw media---are the default artifacts for coordination and audit.

\textbf{Privacy-preserving semantic abstraction.}
Edge nodes enforce ephemeral buffers and fail-closed publication rules aligned with Box~1.
Storage systems (NAS) hold audit logs, configuration, and governance records---not default video archives.

\textbf{Energy efficiency and maintainability.}
PoE reduces cabling complexity; semi-industrial fanless edge units suit school comms closets;
reference models are replaceable within class without single-vendor lock-in.

\textbf{Edge resilience and degraded mode.}
UPS-backed nodes, VLAN segmentation, and lockable cabinets support continued manual SMS if automation
is unavailable---without mandating cloud video failover.

\textbf{Horizon Europe scalability.}
Documented Tier~B/C BOM lines enable comparable replication across consortium partners;
optional federation (Category~L) exports \textbf{anonymized aggregate metrics only} and remains
\textbf{disabled by default}.

\subsection{Recommended procurement strategy}

\begin{enumerate}[noitemsep]
  \item Start with \textbf{Tier~A sandbox / tabletop hardware} before occupant live sensing.
  \item Validate governance, DPIA acceptance, and protocol mapping before camera activation.
  \item Reuse existing school ONVIF cameras \textbf{only} after DPIA scope review and steering approval.
  \item Prefer \textbf{PoE} and \textbf{VLAN-capable} switches and firewalls already supported by school IT.
  \item Avoid cloud-dependent cameras and NVRs that require off-site raw video retention.
  \item Do not procure biometric analytics, facial recognition, or voiceprint appliances.
  \item Purchase \textbf{UPS} and \textbf{lockable cabinets} early in Phase~1 infrastructure validation.
  \item Keep GPU / Jetson procurement \textbf{proportional} to co-designed zone count.
  \item Separate \textbf{research export hardware} (Category~L) from operational safety infrastructure.
  \item Require \textbf{acceptance tests} (below) before go-live sign-off.
\end{enumerate}

\subsection{Acceptance tests before go-live}

Institutional IT and the DPO should witness or review evidence for:

\begin{table}[htbp]
  \centering
  \caption{Pre-go-live acceptance tests (indicative checklist).}
  \label{tab:acceptance-tests}
  \small
  \begin{tabular}{@{}p{4.2cm}p{7.8cm}@{}}
    \toprule
    Test & Pass criterion \\
    \midrule
    No raw media egress &
      Packet capture / config audit shows no persistent video/audio upload paths. \\
    No biometric modules &
      Software inventory and event schema attest no FR, voiceprint, or profiling modules. \\
    VLAN segmentation &
      Sensing, coordination, staff, and management networks isolated per trust-zone plan. \\
    Local processing only &
      Edge nodes process zones on premises; coordination host on school LAN. \\
    Event-only publication &
      Durable store contains structured summaries and audit logs only (DPIA-aligned). \\
    Dashboard access control &
      RBAC + MFA for privileged roles; safety officer accounts provisioned. \\
    Audit logging &
      Disposition and override events recorded and searchable. \\
    UPS graceful shutdown &
      Test shutdown script; documented autonomy time $\geq$ agreed minimum. \\
    Degraded-mode runbook &
      Manual SMS fallback exercised in tabletop and IT drill. \\
    DPIA evidence pack &
      Checklist Section~\ref{sec:dpia} items complete; steering sign-off recorded. \\
    \bottomrule
  \end{tabular}
\end{table}

Cross-reference: operational go/no-go gates Section~\ref{sec:pilot-programme}; trust zones
Table~\ref{tab:trust-zones}; full BOM tables
Tables~\ref{tab:bom-tier-a}--\ref{tab:bom-tier-c}.
