\section{Indicative Budget Ranges}
\label{app:budget}
\label{sec:budget-ranges}

Figures are \textbf{order-of-magnitude} ranges for European school pilots (planning basis).
Detailed bill-of-materials: \textbf{Appendix~E} (Tables~\ref{tab:bom-tier-a}--\ref{tab:bom-tier-c}).
Not binding quotes or Horizon budget submissions.

\smallskip\noindent\textit{Prices are approximate EUR ranges and vary by country, taxes, availability,
procurement framework, educational discounts, and vendor agreements.
Final purchasing decisions require institutional IT and procurement validation.}

\subsection{CapEx by deployment tier (EUR, indicative)}

\begin{table}[htbp]
  \centering
  \caption{CapEx ranges aligned with Appendix~E hardware tiers.}
  \label{tab:capex-by-tier}
  \small
  \begin{tabular}{@{}lrrl@{}}
    \toprule
    Tier & Low & High & Scope \\
    \midrule
    A --- Minimal (Table~\ref{tab:bom-tier-a}) & 8{,}000 & 20{,}000 & 1 school; 2--6 zones \\
    B --- Horizon (Table~\ref{tab:bom-tier-b}) & 25{,}000 & 90{,}000 & 1--3 schools; 10--20 zones \\
    C --- Multi-site (Table~\ref{tab:bom-tier-c}) & 100{,}000 & 350{,}000 & 5--10 schools; federation \\
    \bottomrule
  \end{tabular}
\end{table}

\textbf{Greenfield vs.\ existing cameras:} schools with compatible PoE plant approach Tier~A lower
bounds; full Tier~B/C greenfield and professional integration approach upper bounds.

\subsection{OpEx --- pilot year 1 (EUR)}

\begin{table}[htbp]
  \centering
  \caption{Indicative OpEx --- Tier~A / MVP annual.}
  \label{tab:opex-mvp}
  \small
  \begin{tabular}{@{}lrr@{}}
    \toprule
    Item & Low & High \\
    \midrule
    Maintenance / support & 2{,}000 & 8{,}000 \\
    Certificates / monitoring & 500 & 2{,}000 \\
    Incremental IT (0.1--0.2 FTE) & 3{,}000 & 8{,}000 \\
    Safety officer pilot time & 2{,}000 & 6{,}000 \\
    Training & 1{,}000 & 4{,}000 \\
    DPO / legal review & 2{,}000 & 10{,}000 \\
    \midrule
    \textbf{Total OpEx} & \textbf{10{,}500} & \textbf{38{,}000} \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Multi-site scaling (indicative)}

\begin{itemize}[noitemsep]
  \item Tier~B (2--3 schools): CapEx within EUR~25{,}000--90{,}000 band; OpEx year~1 EUR~25{,}000--80{,}000.
  \item Tier~C (5--10 schools): CapEx EUR~100{,}000--350{,}000; OpEx EUR~80{,}000--250{,}000.
  \item Horizon research staff and evaluation costs are proposal-specific and separate from SMS operations.
\end{itemize}

Financial ROI on safety outcomes is \textbf{not} claimed.
