\section{Reference Technical Architecture}
\label{app:technical-architecture}

This appendix supplies \textbf{implementation reference material} for school IT teams,
integrators, and research engineers.
It does not alter governance boundaries in the main document: advisory-only outputs,
no biometrics, no autonomous enforcement, and no raw-media egress remain mandatory.

\subsection{Logical Component Topology}

Reference on-premises roles (engineering view):

\begin{enumerate}[noitemsep]
  \item \textbf{Edge nodes} --- ephemeral perception, privacy runtime, semantic event publication.
  \item \textbf{Local event bus} --- NATS (preferred) or MQTT broker on school infrastructure.
  \item \textbf{Local orchestrator} --- fusion, temporal safety graph, constrained decision
        support, human-in-the-loop recommendation generation.
  \item \textbf{Staff dashboard API} --- review queues, event timeline, audit views.
  \item \textbf{Optional research server} --- anonymized metrics only; disabled by default.
\end{enumerate}

Only JSON semantic event records, health telemetry, audit entries, and recommendation
metadata are permitted on the bus---never raw video or audio payloads.

\subsection{Edge Node Engineering Responsibilities}

Per edge node (reference split):
\begin{itemize}[noitemsep]
  \item ingest camera/audio/sensor streams on local sensing VLAN;
  \item enforce buffer TTL (default 30 seconds; change requires governance approval);
  \item reject forbidden egress fields (raw video/audio, image payloads, biometric identifiers);
  \item publish to subject pattern \texttt{dualexis.events.\{site\_id\}.\{zone\_id\}};
  \item emit health heartbeats to \texttt{dualexis.health.\{node\_id\}}.
\end{itemize}

Edge nodes do not run multimodal fusion, graph maintenance, or unconstrained generative
reasoning in the reference architecture.

\subsection{Privacy Manifest Defaults (Reference)}

\begin{itemize}[noitemsep]
  \item \texttt{allow\_persistent\_media: false}
  \item \texttt{allow\_biometric\_features: false}
  \item \texttt{allow\_identity\_linking: false}
  \item \texttt{policy\_id: strict-v1}
\end{itemize}

\subsection{Orchestrator Engineering Responsibilities}

\begin{itemize}[noitemsep]
  \item subscribe to semantic event streams via queue group \texttt{dualexis-orchestrator};
  \item maintain zone-centric temporal safety graph;
  \item generate advisory recommendations with mandatory review flags;
  \item publish audit entries to \texttt{dualexis.audit.\{site\_id\}};
  \item expose REST API for dashboard integration on orchestrator VLAN;
  \item fan-out via queue group \texttt{dualexis-api} where applicable.
\end{itemize}

\subsection{Reference VLAN Model}

\begin{table}[htbp]
  \centering
  \caption{Reference VLAN segmentation (adjust to site standards).}
  \label{tab:vlan-model-appendix}
  \small
  \begin{tabular}{@{}p{2.8cm}p{3.4cm}p{5.8cm}@{}}
    \toprule
    VLAN & Members & Notes \\
    \midrule
    CAM-AUDIO &
      Cameras, microphones, edge nodes &
      No Internet; RTSP/audio ingest only. \\
    EDGE-MGMT &
      Edge orchestration agents &
      SSH/admin from jump host only. \\
    EVENT-BUS &
      NATS/MQTT cluster &
      TLS recommended; mutual TLS for extended pilot. \\
    ORCH &
      Local orchestrator, graph store &
      Subscribes to bus; no camera access. \\
    DASHBOARD &
      API, staff UI hosts &
      HTTPS; SSO integration. \\
    RESEARCH (opt.) &
      Metrics collector &
      Egress firewall; anonymized data only. \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Event Bus: NATS and MQTT}

\textbf{Primary recommendation:} NATS with JetStream disabled or minimally configured for
pilot (ephemeral semantics preferred).

Subject namespace (NATS):
\begin{itemize}[noitemsep]
  \item \texttt{dualexis.events.\{site\_id\}.\{zone\_id\}} --- semantic events;
  \item \texttt{dualexis.audit.\{site\_id\}} --- audit trail;
  \item \texttt{dualexis.health.\{node\_id\}} --- edge health;
  \item \texttt{dualexis.recommendations.\{site\_id\}} --- advisory outputs.
\end{itemize}

\textbf{MQTT alternative:} equivalent topic hierarchy with QoS~1, \texttt{retained=false},
TLS on broker, and client certificates for extended pilot.

\subsection{Firewall and Routing Rules (Reference)}

\begin{itemize}[noitemsep]
  \item CAM-AUDIO $\rightarrow$ EDGE-MGMT: management ports only;
  \item EDGE nodes $\rightarrow$ EVENT-BUS: publish semantic events and health;
  \item ORCH $\rightarrow$ EVENT-BUS: subscribe/publish;
  \item DASHBOARD $\rightarrow$ ORCH API: HTTPS only;
  \item deny all Internet egress from CAM-AUDIO and EVENT-BUS;
  \item RESEARCH VLAN egress allowlist documented if enabled.
\end{itemize}

\subsection{DNS, Time, and Certificates}

\begin{itemize}[noitemsep]
  \item NTP synchronization across edge and orchestrator (critical for event ordering);
  \item internal DNS or static hosts for bus and API endpoints;
  \item TLS certificates from school PKI or documented internal CA;
  \item certificate rotation procedure in operational runbooks.
\end{itemize}

\subsection{Bandwidth Planning (Indicative)}

\begin{itemize}[noitemsep]
  \item peak 1--20 structured events/s per site during stress exercises (pilot estimate);
  \item health telemetry $<$ 1 Mbps aggregate;
  \item dashboard API traffic negligible on LAN;
  \item video streams remain on camera VLAN to edge nodes only.
\end{itemize}

\subsection{Reference Edge Hardware Tiers}

\begin{table}[htbp]
  \centering
  \caption{Reference edge node hardware tiers (indicative procurement).}
  \label{tab:edge-hardware-appendix}
  \small
  \begin{tabular}{@{}p{2.4cm}p{3.6cm}p{3.6cm}p{3.2cm}@{}}
    \toprule
    Tier & CPU & Memory & Storage \\
    \midrule
    Edge-S (sensor/audio) &
      4--8 cores, x86\_64 &
      16 GB RAM &
      256 GB NVMe (OS + logs; no media store) \\
    Edge-V (video-light) &
      8 cores &
      32 GB RAM &
      512 GB NVMe \\
    Edge-G (video + GPU) &
      8+ cores &
      32--64 GB RAM &
      512 GB--1 TB NVMe \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{GPU Options (Video Perception)}

GPU acceleration is recommended for video-heavy edge nodes; optional for audio/sensor-only nodes.

\begin{itemize}[noitemsep]
  \item \textbf{Supported class:} NVIDIA edge/datacenter GPUs with current driver support
        (e.g., T4, L4, A2, RTX A4000 class---exact SKU subject to procurement and thermal limits).
  \item \textbf{Minimum VRAM:} 8 GB single-stream prototypes; 16 GB preferred multi-stream pilots.
  \item \textbf{Deployment:} container runtime with GPU reservation; GPU not required on orchestrator
        for MVP if abstraction completes at edge.
  \item \textbf{Fallback:} CPU-only perception with reduced streams; document in runbooks.
\end{itemize}

\subsection{Orchestrator Host Minimum Specification}

\begin{table}[htbp]
  \centering
  \caption{Local orchestrator / API host (single-site MVP).}
  \label{tab:orchestrator-hardware-appendix}
  \small
  \begin{tabular}{@{}ll@{}}
    \toprule
    Component & Minimum specification \\
    \midrule
    CPU & 8--16 cores \\
    RAM & 32--64 GB \\
    Storage & 1 TB NVMe (events, graph, audit; encryption at rest recommended) \\
    GPU & Optional for local reasoning pilots; CPU acceptable for MVP \\
    Redundancy & Hot standby recommended extended pilot; single node MVP \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Camera and Stream Integration}

\begin{itemize}[noitemsep]
  \item RTSP or ONVIF-compatible streams into ephemeral pipeline;
  \item resolution typically 720p--1080p for zone-level descriptors;
  \item container runtime with optional GPU device reservation.
\end{itemize}

\subsection{Bus Cluster Sizing and Backup}

\begin{itemize}[noitemsep]
  \item MVP: single broker acceptable;
  \item extended pilot: three-node cluster optional;
  \item backup orchestrator state (graph, audit) per retention policy;
  \item indicative RTO 4--24 h for MVP (agree with school IT).
\end{itemize}
