\section{Budget Ranges (Indicative Planning)}
\label{sec:budget-ranges}

\subsection{Disclaimer}

Figures below are \textbf{order-of-magnitude ranges} for institutional budgeting discussions
in European school pilot contexts (2025--2026 planning basis).
Actual costs depend on procurement channels, existing infrastructure, VAT, labor rates, and
scope.
They exclude ongoing school staff salaries except where noted as incremental effort.

This section does not constitute a funding guarantee or Horizon Europe budget submission.

\subsection{Capital Expenditure (CapEx) --- MVP (1 School)}

\begin{table}[htbp]
  \centering
  \caption{Indicative CapEx ranges --- MVP single site (EUR).}
  \label{tab:capex-mvp}
  \small
  \begin{tabular}{@{}lrr@{}}
    \toprule
    Item & Low & High \\
    \midrule
    Edge node hardware (1--2 units, CPU) & 2{,}000 & 6{,}000 \\
    Edge GPU upgrade (optional, 1 unit) & 1{,}500 & 4{,}000 \\
    Orchestrator server & 3{,}000 & 8{,}000 \\
    UPS and networking (switches, cabling) & 1{,}000 & 5{,}000 \\
    Camera/audio upgrades (if needed) & 0 & 15{,}000 \\
    Installation and mounting & 1{,}000 & 4{,}000 \\
    \midrule
    \textbf{Total CapEx (MVP)} & \textbf{7{,}500} & \textbf{42{,}000} \\
    \bottomrule
  \end{tabular}
\end{table}

Schools with existing compatible cameras may approach the lower bound.

\subsection{Operational Expenditure (OpEx) --- MVP (Annualized)}

\begin{table}[htbp]
  \centering
  \caption{Indicative OpEx ranges --- MVP annual (EUR).}
  \label{tab:opex-mvp}
  \small
  \begin{tabular}{@{}lrr@{}}
    \toprule
    Item & Low & High \\
    \midrule
    Maintenance and support contract & 2{,}000 & 8{,}000 \\
    SSL/certificates and monitoring tools & 500 & 2{,}000 \\
    Incremental IT effort (0.1--0.2 FTE) & 3{,}000 & 8{,}000 \\
    Incremental safety officer pilot time & 2{,}000 & 6{,}000 \\
    Training delivery and materials & 1{,}000 & 4{,}000 \\
    DPO / legal review (external counsel optional) & 2{,}000 & 10{,}000 \\
    \midrule
    \textbf{Total OpEx (MVP, year 1)} & \textbf{10{,}500} & \textbf{38{,}000} \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Recommended Pilot (1--3 Schools)}

Scaling guidance:
\begin{itemize}[noitemsep]
  \item add approximately 60--80\% of MVP CapEx per additional school with similar zone count;
  \item shared research and governance costs across sites;
  \item central orchestration optional per site (recommended: per-site orchestrator for resilience).
\end{itemize}

Indicative total CapEx: EUR~15{,}000--EUR~90{,}000.

Indicative year-1 OpEx: EUR~25{,}000--EUR~80{,}000 (includes evaluation and training).

\subsection{Extended Pilot (5--10 Schools)}

Indicative total CapEx: EUR~60{,}000--EUR~350{,}000.

Indicative year-1 OpEx: EUR~80{,}000--EUR~250{,}000.

Includes hardened bus cluster, federated metrics infrastructure, and multi-site coordination.

\subsection{Research and Horizon Europe Components (Optional)}

Separate research budget lines (not required for operational SMS integration):
\begin{itemize}[noitemsep]
  \item researcher effort for evaluation and publication;
  \item ethics-approved study instruments;
  \item anonymized cross-site analysis infrastructure;
  \item consortium management and harmonization workshops.
\end{itemize}

Indicative Horizon-scale project budgets are proposal-specific and not estimated here.

\subsection{Value Considerations (Non-Financial)}

Institutions should weigh:
\begin{itemize}[noitemsep]
  \item privacy-preserving alternative to clip-archive expansion;
  \item auditability for governance and insurance discussions;
  \item research partnership value with UCJC/SEK and EU consortia;
  \item staff training assets reusable across sites.
\end{itemize}

Financial ROI on safety outcomes is \textbf{not} claimed in this document.
