\section{Conclusion and Next Steps}
\label{sec:conclusion-req}

This document specifies practical, governance-aware requirements for pilot deployment
of DUALEXIS in schools and confined educational spaces.
It supports structured dialogue with school leadership, UCJC/SEK stakeholders, IT and
data protection officers, and potential Horizon Europe partners.

\subsection{Summary of Requirements}

\begin{itemize}[noitemsep]
  \item \textbf{Local, privacy-preserving processing} with structured semantic events only on
        approved internal channels.
  \item \textbf{Explicit exclusions:} no facial recognition, biometrics, raw media storage
        by default, or autonomous enforcement.
  \item \textbf{Human-in-the-loop} operator workflows integrated with existing emergency protocols.
  \item \textbf{Segmented school network} architecture with edge nodes, local orchestrator,
        dashboard, and audit logs.
  \item \textbf{Phased pilots:} MVP (1 school), recommended (1--3 schools), extended (5--10 schools).
  \item \textbf{Governance gates:} DPIA checklist, transparency, training, and ethics review
        before live sensing.
  \item \textbf{Evaluation plan} focused on situational awareness support and privacy posture,
        not claimed operational effectiveness.
\end{itemize}

\subsection{What This Document Does Not Provide}

\begin{itemize}[noitemsep]
  \item legal certification of GDPR or AI Act compliance;
  \item evidence of safety outcome improvements;
  \item binding cost quotes or procurement commitments;
  \item approval to process personal data without institutional authorization.
\end{itemize}

\subsection{Recommended Next Steps for Stakeholders}

\paragraph{School leadership.}
Form pilot steering committee; approve scope and transparency plan; schedule protocol mapping workshop.

\paragraph{Data protection officer.}
Initiate DPIA using Section~\ref{sec:dpia} checklist; review retention and lawful basis.

\paragraph{IT department.}
Approve trust-zone diagram and data-flow rules; implement reference architecture
(Appendix~\ref{app:technical-architecture}); define certificate and backup policies.

\paragraph{Safety officers.}
Co-design protocol mapping matrix; participate in training and tabletop exercises.

\paragraph{UCJC / research team.}
Provide sandbox deployment support; harmonize evaluation metrics for consortium proposals.

\paragraph{Horizon Europe partners.}
Align on common semantic schemas, governance templates, and multi-site reporting boundaries.

\subsection{Document Maintenance}

Version 0.1 reflects the DUALEXIS open-source reference architecture and infrastructure
manifests as of the document date.
Updates will be version-controlled with the research repository.
Institutions should maintain site-specific annexes (network diagrams, signed mappings, DPIA records)
as controlled documents separate from this general requirements baseline.

\vspace{1em}
\noindent\textbf{Contact.} For pilot discussions through UCJC/CRIA-BDHS, use the corresponding
author contacts listed on the title page.
