\section{Data Protection Impact Assessment Checklist}
\label{sec:dpia}

\subsection{Purpose}

This section provides a \textbf{DPIA preparation checklist} for school pilots.
It supports discussions with data protection officers and ethics committees.
Completion of this checklist does \textbf{not} certify GDPR compliance or replace a
formal DPIA signed by the institution.

\subsection{When a DPIA Is Likely Required}

A DPIA is typically indicated when processing involves:
\begin{itemize}[noitemsep]
  \item systematic monitoring of publicly accessible areas in schools;
  \item technologies that may affect children at scale;
  \item novel AI-assisted decision support in safety contexts;
  \item combined audio-visual processing even without identity recognition.
\end{itemize}

Institutions should consult supervisory authority guidance and national education-sector norms.

\subsection{DPIA Checklist}

\begin{longtable}{@{}p{0.6cm}p{5.2cm}p{6.8cm}@{}}
\toprule
\# & Item & Evidence / deliverable \\
\midrule
\endhead
1 & Processing description &
  Written summary of zones, modalities, event types, retention, recipients. \\
2 & Necessity \& proportionality &
  Rationale vs.\ manual-only awareness; alternatives considered. \\
3 & No biometrics attestation &
  Architecture review confirming FR/biometric modules absent. \\
4 & No raw media retention &
  TTL configuration, storage audit procedure, forbidden egress fields. \\
5 & Lawful basis &
  DPO/legal memo documenting chosen GDPR basis. \\
6 & Children's data safeguards &
  Guardian communication plan, access restrictions. \\
7 & Risk identification &
  Link to risk register (Section~\ref{sec:risk-register}). \\
8 & Mitigation measures &
  Segmentation, RBAC, audit, training, review gates. \\
9 & Consultation &
  Staff union / works council / parent council as required locally. \\
10 & Residual risk acceptance &
  Signed acceptance by school leadership and DPO. \\
11 & Review schedule &
  DPIA review trigger events (scope change, incident, new modality). \\
12 & Processor agreements &
  DPAs with research and IT vendors. \\
13 & Breach response &
  Integration with school incident response plan. \\
14 & Data subject rights &
  Procedure for requests via school DPO. \\
15 & Transparency materials &
  Published notices and signage records. \\
\bottomrule
\end{longtable}

\subsection{Documentation Pack for Institutional Review}

Recommended submission bundle:
\begin{itemize}[noitemsep]
  \item this requirements document;
  \item network diagram and VLAN table;
  \item protocol mapping matrix;
  \item transparency notices and training outline;
  \item evaluation plan and ethics approval (if human-subjects components);
  \item signed governance charter.
\end{itemize}

\subsection{Post-Pilot Review}

After MVP or recommended pilot completion:
\begin{itemize}[noitemsep]
  \item DPIA update if scope, retention, or modalities change;
  \item lessons learned report for governance board;
  \item decision record: extend, modify, or terminate processing.
\end{itemize}
