\section{On-Premises Deployment Architecture}
\label{sec:edge-infrastructure-req}

\subsection{Institutional Deployment Concept}

Each pilot site operates DUALEXIS \textbf{entirely on school-controlled infrastructure}.
The architecture separates \emph{what the institution needs to govern} from \emph{how IT
implements it} (Appendix~\ref{app:technical-architecture}).

Four logical roles support safety management workflows:

\begin{enumerate}[noitemsep]
  \item \textbf{Zone processing units} --- local perception and privacy enforcement at
        approved monitoring zones; ephemeral sensing only.
  \item \textbf{Site coordination service} --- fusion of zone reports, temporal emergency
        context, advisory recommendation drafts, and staff review interfaces.
  \item \textbf{Staff decision-support interface} --- review queues, zone timelines, and
        audit views for licensed safety personnel.
  \item \textbf{Optional research export} (disabled by default) --- anonymized evaluation
        metrics only; no operational control authority.
\end{enumerate}

\textbf{Critical boundary:} raw video and audio do not leave zone processing units as
persistent records.
Only structured, zone-level semantic safety events and governance metadata cross internal
operational boundaries.

\subsection{Governance Responsibilities by Role}

\begin{table}[htbp]
  \centering
  \caption{Deployment roles and institutional accountability (MVP pilot).}
  \label{tab:deployment-roles}
  \small
  \begin{tabular}{@{}p{3.0cm}p{5.2cm}p{4.8cm}@{}}
    \toprule
    Role & Institutional function & Must not \\
    \midrule
    Zone processing &
      Convert ephemeral sensing to zone-level events under privacy policy &
      Store raw media; perform site-wide review or protocol activation \\
    Site coordination &
      Maintain shared situational picture; queue advisories for human review &
      Dispatch emergency services; trigger lockdown autonomously \\
    Staff interface &
      Support comprehension, disposition, and audit &
      Present outputs as mandatory orders; enable biometric review panels \\
    Research export (opt.) &
      Receive pre-approved anonymized metrics &
      Receive operational control or identity-linked records \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Privacy Policy Defaults}

Reference deployments use a \textbf{strict privacy profile} by default:
\begin{itemize}[noitemsep]
  \item no persistent media retention;
  \item no biometric or identity-linking features enabled;
  \item short-lived ephemeral buffers only;
  \item purpose limited to safety coordination and accountability records.
\end{itemize}

Any relaxation requires documented governance approval, DPIA update, and ethics review
where applicable.

\subsection{Audit and Accountability}

Audit records must support institutional oversight without reproducing raw sensing:
\begin{itemize}[noitemsep]
  \item append-only log of privacy checks, review dispositions, and policy changes;
  \item timestamps and staff \emph{role} identifiers---not student identity;
  \item retention period defined in the site DPIA (indicative pilot range: 90--365 days,
        subject to counsel);
  \item export for DPO and steering-committee review; tamper-evidence recommended for
        extended phases.
\end{itemize}

\subsection{Staff Decision-Support Interface (Requirements)}

The staff-facing system must support \textbf{human-in-the-loop} emergency coordination:

\begin{table}[htbp]
  \centering
  \caption{Decision-support interface requirements (non-technical summary).}
  \label{tab:dashboard-req}
  \small
  \begin{tabular}{@{}p{3.2cm}p{8.8cm}@{}}
    \toprule
    Capability & Requirement \\
    \midrule
    Zone timeline &
      Chronological semantic events by zone and severity for risk communication. \\
    Review queue &
      Pending advisories with explanations; approve, dismiss, or escalate (advisory only). \\
    Context summary &
      Multi-zone situation view for comprehension---no person-tracking graph. \\
    System health &
      Visibility that zone units and coordination service are operating normally. \\
    Audit access &
      Searchable trail for administrators and DPO review. \\
    Prohibitions &
      No raw video playback by default; no biometric or identity panels. \\
    Access control &
      Role-based access (safety officer, administrator, auditor, read-only). \\
    \bottomrule
  \end{tabular}
\end{table}

Authentication should integrate with the school identity system where available.
Multi-factor authentication is recommended for privileged roles.

\subsection{Optional Research Export}

When explicitly authorized for evaluation studies:
\begin{itemize}[noitemsep]
  \item only anonymized aggregate metrics leave the site;
  \item no free-text occupant descriptors unless separately approved;
  \item physically or logically separated from operational safety workflows;
  \item not required for day-to-day emergency coordination.
\end{itemize}

Technical messaging patterns, host specifications, and engineering manifests are documented
in Appendix~\ref{app:technical-architecture}.
