\section{Evaluation Plan and Metrics}
\label{sec:evaluation-metrics}

\subsection{Evaluation Stance}

Pilot evaluation assesses \textbf{governance feasibility}, \textbf{operator workflow
utility}, and \textbf{privacy posture} under controlled conditions.
It does \textbf{not} claim validated reductions in harm or emergency outcomes unless
appropriately designed longitudinal studies are approved and executed.

Synthetic scaffold metrics from the research framework (Table references in companion
publications) support pre-pilot replication only; field metrics below apply to governed pilots.

\subsection{Metric Categories}

\begin{table}[htbp]
  \centering
  \caption{Pilot evaluation metric categories.}
  \label{tab:eval-metrics}
  \small
  \begin{tabular}{@{}p{3.0cm}p{4.4cm}p{4.6cm}@{}}
    \toprule
    Category & Example metrics & Method \\
    \midrule
    Situational awareness &
      Comprehension scores, SA questionnaires~\cite{endsley1995sa} &
      Tabletop + live exercises \\
    Operator workflow &
      Time-to-review, disposition rates, override frequency &
      Dashboard logs \\
    Risk communication &
      Clarity ratings of explanations &
      Staff surveys (ethics approved) \\
    Privacy &
      Policy violations, retention audits, egress tests &
      Technical audit \\
    Technical &
      End-to-end latency, node availability, bus uptime &
      Telemetry \\
    Protocol alignment &
      Mapping correctness in exercises &
      Structured debrief \\
    Workload &
      Review queue depth, alert fatigue indicators &
      Logs + interviews \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Baseline Comparisons (Optional)}

Where ethically permissible, compare:
\begin{itemize}[noitemsep]
  \item advisory semantic workflow vs.\ manual-only awareness in tabletop conditions;
  \item structured events vs.\ clip-based review counterfactual (documented simulation, not live FR).
\end{itemize}

No ranking or superiority claims without pre-registered inferential design.

\subsection{Data Collection and Minimization}

\begin{itemize}[noitemsep]
  \item collect minimum logs necessary for evaluation;
  \item anonymize staff survey responses where possible;
  \item no student-identifiable data in evaluation corpora;
  \item separate operational logs from research datasets with access controls;
  \item retention schedule approved by DPO.
\end{itemize}

\subsection{Reporting Cadence}

\begin{itemize}[noitemsep]
  \item weekly operational metrics (internal steering);
  \item monthly governance summary (incidents, false alarms, training);
  \item end-of-phase report for MVP / recommended / extended tiers;
  \item peer-reviewed publication only after ethics-approved analysis.
\end{itemize}

\subsection{Horizon Europe Alignment}

For consortium proposals, harmonize:
\begin{itemize}[noitemsep]
  \item common metric definitions across partner schools;
  \item anonymized cross-site aggregate reporting template;
  \item open replication package (synthetic seeds + governance templates);
  \item explicit separation of operational SMS integration vs.\ research objectives.
\end{itemize}
