\section{Pilot Programme, Timeline, and Governance Gates}
\label{sec:pilot-programme}
\label{sec:pilot-methodology}
\label{sec:implementation-plan}

\subsection{Phased participation (gated)}

No live occupant sensing until documented governance approval.
Phases expand only after prior gates are met.

\begin{table}[htbp]
  \centering
  \caption{Pilot phases and institutional focus.}
  \label{tab:pilot-phases}
  \small
  \begin{tabular}{@{}p{1.2cm}p{2.0cm}p{5.8cm}@{}}
    \toprule
    Phase & Scale & Focus \\
    \midrule
    0 & Requirements &
      Stakeholder alignment; zone mapping; DPIA initiation; co-design workshop. \\
    1 & Sandbox &
      Isolated network; synthetic feeds; training; \textbf{two tabletop exercises}; no live public sensing. \\
    2 & MVP &
      1 school, 2--4 zones; staffed-hours review; weekly calibration. \\
    3 & Recommended &
      1--3 schools; ethics-approved staff feedback; consortium learning report (anonymized). \\
    4 & Extended &
      5--10 schools; harmonized reporting; optional anonymized cross-site metrics. \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Co-design, opt-out, and community participation}

\textbf{Co-design.} Schools co-define monitored zones with safety staff, leadership, and---where
required---parent or student representatives.
Zone lists are reviewed before each phase; cafeterias and sensitive areas require explicit approval.

\textbf{Phased participation.} Institutions may pause at Phase~1 indefinitely; Phase~2+ requires
completed tabletop exercises and steering-committee authorization.

\textbf{Opt-out and scope reduction.} Any zone may be excluded or sensing paused without ending the
whole programme, subject to steering-committee and DPO review.
Stakeholder withdrawal or regulatory inquiry triggers stop conditions below.

\subsection{MVP configuration (institutional summary)}

\begin{table}[htbp]
  \centering
  \caption{MVP minimum (planning).}
  \label{tab:mvp-config}
  \small
  \begin{tabular}{@{}ll@{}}
    \toprule
    Element & MVP minimum \\
    \midrule
    Schools & 1 \\
    Zones & 2--4 \\
    Zone processing units & 1--2 \\
    Site coordination & 1 on-premises host \\
    Staff dashboard & 1 interface \\
    Research export & Disabled \\
    Incremental staff effort & 0.2--0.5 safety FTE; 0.1 IT FTE (indicative) \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Indicative timeline (single school)}

\begin{table}[htbp]
  \centering
  \caption{MVP implementation timeline (planning estimates).}
  \label{tab:timeline}
  \small
  \begin{tabular}{@{}p{2.2cm}p{5.4cm}p{3.4cm}@{}}
    \toprule
    Period & Activities & Lead \\
    \midrule
    Wks 1--4 & Workshops; zone mapping; IT survey & Leadership + research \\
    Wks 5--8 & DPIA; ethics; protocol mapping & DPO + safety \\
    Wks 9--12 & Procurement; network segmentation; install & School IT \\
    Wks 13--16 & Sandbox; synthetic feeds & IT + research \\
    Wks 17--20 & Training; \textbf{tabletop exercises} & Safety + research \\
    Wks 21--36 & MVP live sensing (staffed hours) & Safety + steering \\
    Wk 37+ & Expand / modify / halt decision & Steering committee \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Work packages and RACI}

\begin{table}[htbp]
  \centering
  \caption{RACI summary (R=Responsible, A=Accountable, C=Consulted, I=Informed).}
  \label{tab:raci}
  \footnotesize
  \begin{tabular}{@{}lcccc@{}}
    \toprule
    Package & School & IT & DPO & UCJC research \\
    \midrule
    Governance & A & C & R & C \\
    Network / data flows & C & R/A & C & C \\
    Infrastructure & C & R & I & C \\
    Software / dashboard & I & R & C & R \\
    Operations / SOP & R/A & C & C & C \\
    Evaluation & C & I & C & R \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Go / no-go gates (before live sensing)}

\begin{enumerate}[noitemsep]
  \item governance charter signed (Appendix~\ref{app:governance-templates});
  \item DPIA residual risk accepted by DPO and leadership;
  \item protocol mapping matrix approved;
  \item training completion $\geq$ 90\% of designated staff;
  \item \textbf{two tabletop exercises} completed with documented remediations;
  \item IT sign-off on trust zones and data-flow rules;
  \item ethics approval for evaluation instruments (if applicable).
\end{enumerate}

\subsection{Stop conditions (immediate pause)}

\begin{itemize}[noitemsep]
  \item privacy-policy violation or raw-media egress detected;
  \item unauthorized access to dashboard or audit logs;
  \item stakeholder withdrawal or regulatory inquiry requiring halt;
  \item false-alarm rate above pre-agreed threshold;
  \item failure to maintain advisory-only use (autonomous actuation attempted).
\end{itemize}

Resumption requires incident review and steering-committee approval.
