\section{Privacy, GDPR, and AI Governance}
\label{sec:privacy-gdpr}

\subsection{Privacy-by-Design Commitments}

DUALEXIS pilot deployments adopt the following \textbf{non-negotiable} constraints:

\begin{itemize}[noitemsep]
  \item \textbf{No facial recognition} and \textbf{no biometric processing};
  \item \textbf{No raw video or raw audio storage by default} (ephemeral buffers with TTL);
  \item \textbf{Zone-level semantic events} as the primary operational artifact;
  \item \textbf{Local processing} on school-controlled infrastructure;
  \item \textbf{Human-in-the-loop} review for elevated severities;
  \item \textbf{Purpose limitation} to safety and emergency coordination only.
\end{itemize}

These are engineering invariants in the reference architecture; they do \textbf{not}
automatically satisfy GDPR or AI Act obligations without institution-specific legal analysis.

\subsection{GDPR Mapping (High-Level Planning Aid)}

\begin{table}[htbp]
  \centering
  \caption{GDPR planning topics (not legal compliance certification).}
  \label{tab:gdpr-topics}
  \small
  \begin{tabular}{@{}p{3.4cm}p{8.6cm}@{}}
    \toprule
    Topic & Pilot planning consideration \\
    \midrule
    Lawful basis &
      Document legitimate interest or public task analysis with DPO; children's data heightened care. \\
    Data minimization &
      Semantic abstraction; no persistent media; retention tags on events. \\
    Purpose limitation &
      Safety coordination only; prohibit secondary analytics. \\
    Storage limitation &
      TTL on buffers; event retention schedule in DPIA. \\
    Integrity \& confidentiality &
      Segmentation, TLS, RBAC, encryption at rest (recommended). \\
    Accountability &
      Audit logs, policy versioning, training records. \\
    DPIA &
      Required for high-risk processing; see Section~\ref{sec:dpia}. \\
    Rights of data subjects &
      Procedures for access/erasure requests via school DPO. \\
    \bottomrule
  \end{tabular}
\end{table}

Legal interpretation must be performed by qualified counsel and the institution's DPO.
This document does not constitute legal advice.

\subsection{EU AI Act Considerations (Planning)}

Depending on deployment context, schools may need to assess:
\begin{itemize}[noitemsep]
  \item whether components qualify as high-risk AI systems in safety-related contexts;
  \item transparency obligations for staff-facing decision support tools;
  \item human oversight measures aligned with L6 review semantics;
  \item documentation and logging for conformity assessment if applicable.
\end{itemize}

Conformity assessment is \textbf{not} claimed in this requirements document.

\subsection{Children and Educational Context}

Processing in schools involving minors requires heightened safeguards~\cite{gdpr2016,mittelstadt2016ethics}:
\begin{itemize}[noitemsep]
  \item transparent communication to guardians and age-appropriate notices where required;
  \item prohibition on profiling and marketing reuse of semantic events;
  \item restricted access roles and periodic access reviews;
  \item evaluation datasets anonymized or synthetic unless explicitly approved.
\end{itemize}

\subsection{Consent and Transparency Requirements}

\begin{enumerate}[noitemsep]
  \item Publish plain-language description of \emph{what is monitored} (zones, not individuals),
        \emph{what is not done} (no facial recognition), and \emph{who can access} outputs.
  \item Display signage at monitored zone entrances where legally required.
  \item Provide contact point for questions (school DPO or designated officer).
  \item Document staff training completion before operational go-live.
  \item Maintain versioned transparency materials aligned with policy changes.
\end{enumerate}

Consent models vary by jurisdiction and lawful basis; schools must select appropriate
legal grounds with counsel---this document does not prescribe a single consent template.

\subsection{Data Processing Agreements}

Where UCJC, SEK, or Horizon partners process data on behalf of schools:
\begin{itemize}[noitemsep]
  \item execute DPAs defining roles (controller/processor/joint controller);
  \item specify subprocessors (hosting, maintenance vendors);
  \item define breach notification timelines and audit rights;
  \item limit cross-border transfers with appropriate safeguards if applicable.
\end{itemize}
