\section{Risk Register}
\label{sec:risk-register}

\subsection{Purpose}

This register supports DPIA preparation and pilot steering discussions.
Residual risks require explicit acceptance by school leadership and DPO.

\begin{longtable}{@{}p{1.0cm}p{3.2cm}p{2.0cm}p{2.0cm}p{4.8cm}@{}}
\toprule
ID & Risk & Likely impact & Initial level & Mitigation \\
\midrule
\endhead
R1 &
  Misinterpretation as surveillance &
  Trust loss &
  High &
  Transparency plan; no FR; signage; staff training. \\
R2 &
  False positive alerts &
  Alert fatigue &
  Medium &
  Calibration reviews; human review gates; tabletop tuning. \\
R3 &
  False negative (missed stress) &
  Safety gap &
  Medium &
  Multimodal fusion; protocol remains manual backstop. \\
R4 &
  Raw media retention failure &
  Privacy breach &
  High &
  TTL enforcement; storage audits; forbidden egress fields. \\
R5 &
  Unauthorized dashboard access &
  Data exposure &
  Medium &
  RBAC, MFA, SSO, audit logging. \\
R6 &
  Integrator adds FR module &
  Scope creep &
  High &
  Architecture review; contract clauses; acceptance tests. \\
R7 &
  Autonomous actuation wired &
  Governance violation &
  High &
  No actuation APIs; SOP; technical inspection. \\
R8 &
  Bus/orchestrator outage &
  Awareness loss &
  Medium &
  Degraded mode SOP; UPS; monitoring. \\
R9 &
  GPU supply / thermal issues &
  Delay &
  Low &
  CPU fallback tier; vendor SLA. \\
R10 &
  Children's data sensitivity &
  Regulatory scrutiny &
  High &
  DPIA; DPO oversight; minimization. \\
R11 &
  Cross-border data transfer &
  Legal risk &
  Medium &
  On-prem default; DPAs; transfer impact assessment if needed. \\
R12 &
  LLM hallucination in explanations &
  Misleading staff &
  Medium &
  Grounding checks; mandatory review; disclaimers in UI. \\
R13 &
  Horizon partner scope drift &
  Governance conflict &
  Medium &
  Consortium charter; change control board. \\
R14 &
  Insufficient staff training &
  Misuse &
  Medium &
  Mandatory training gates before go-live. \\
R15 &
  Community opposition &
  Pilot halt &
  Medium &
  Early stakeholder engagement; ethics consultation. \\
\bottomrule
\end{longtable}

\subsection{Risk Review Cadence}

Review register at monthly steering meetings and after any incident.
Escalate High residual risks to leadership before phase transitions.
