\section{Safety Use Cases and Protocol Mapping}
\label{sec:safety-use-cases}

\subsection{Design Principle}

DUALEXIS outputs \textbf{advisory semantic events} and recommendations.
Schools retain authority to activate lockdown, evacuation, or verification procedures through
existing emergency systems.
Semantic event types must be mapped to institutional protocols \emph{before} live sensing.

\subsection{Priority Use Cases (Initial Pilot)}

\begin{table}[htbp]
  \centering
  \caption{Priority safety use cases and illustrative semantic event themes.}
  \label{tab:use-cases}
  \small
  \begin{tabular}{@{}p{3.2cm}p{4.2cm}p{4.6cm}@{}}
    \toprule
    Use case & Scenario theme & Operator need \\
    \midrule
    Exit impairment &
      Blocked or congested egress &
      Identify affected zones/routes; advise verification. \\
    Crowd stress &
      Abnormal density or flow &
      Early awareness before escalation. \\
    Multimodal conflict &
      Disagreement across audio/video/sensor cues &
      Structured fusion summary for review. \\
    Evacuation support &
      Route availability, assembly context &
      Zone-level guidance inputs (advisory). \\
    Nominal monitoring &
      Baseline flow patterns &
      Reduce false alarms; calibration reference. \\
    Audio stress indicator &
      Non-speech acoustic stress proxies &
      Zone-level indicator only; no speaker ID. \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Explicitly Excluded Use Cases}

\begin{itemize}[noitemsep]
  \item student or staff identification and attendance tracking;
  \item behavioral discipline scoring or predictive sanctioning;
  \item forensic person search from stored video;
  \item automated emergency service dispatch;
  \item psychological or mental-health inference from sensor streams.
\end{itemize}

\subsection{Human-in-the-Loop Review}

Events at medium severity and above default to \textbf{mandatory human review}.
Review queues present:
\begin{itemize}[noitemsep]
  \item zone identifier and timestamp;
  \item severity and confidence;
  \item explanation text referencing structured evidence fields;
  \item recommended advisory action (\emph{monitor}, \emph{notify staff}, \emph{request review},
        \emph{escalate});
  \item disposition state (pending, in progress, dismissed, escalated).
\end{itemize}

Staff disposition is logged for audit; external actions (PA announcements, calling emergency
services) occur outside DUALEXIS.

\subsection{Protocol Mapping Workshop (Required)}

Before MVP go-live, conduct a facilitated workshop covering:
\begin{enumerate}[noitemsep]
  \item existing lockdown, evacuation, and shelter-in-place procedures;
  \item mapping from semantic event types to protocol decision trees;
  \item roles and escalation paths (on-site lead, administration, external services);
  \item communication templates for staff and community transparency;
  \item false-alarm handling and calibration review cadence.
\end{enumerate}

Deliverable: signed protocol mapping matrix stored with pilot governance records.
