\subsection{Formal Human-AI Governance State Machine}
\label{sec:formal-governance-model}

\eswareponame{} positions human oversight as a \textbf{formal governance framework for high-risk
decision support systems}, not an informal review flag. The macro-state space is
\begin{equation*}
  S = \{s^{AI}, s^{H}, s^{I}\}
\end{equation*}
corresponding to \emph{AI recommendation}, \emph{human review}, and
\emph{institutional escalation} phases. The transition alphabet is
$\Sigma = \{\mathrm{issue}, \mathrm{accept}, \mathrm{override}, \mathrm{dismiss},
\mathrm{escalate}, \mathrm{close}\}$.

\paragraph{Transition function.}
The deterministic transition function $\delta: S \times \Sigma \rightarrow S$ is
defined on the documented domain by:
\begin{align*}
  \delta(\mathit{ai_recommendation}, \mathit{issue}) &= \mathit{human_review} \\
  \delta(\mathit{human_review}, \mathit{accept}) &= \mathit{human_review} \\
  \delta(\mathit{human_review}, \mathit{override}) &= \mathit{human_review} \\
  \delta(\mathit{human_review}, \mathit{dismiss}) &= \mathit{human_review} \\
  \delta(\mathit{human_review}, \mathit{escalate}) &= \mathit{institutional_escalation} \\
  \delta(\mathit{institutional_escalation}, \mathit{close}) &= \mathit{institutional_escalation}
\end{align*}
High-severity recommendations initialise at $s^{AI}$.
Transition $\tau_{\mathrm{issue}}$ moves the artefact to $s^{H}$ when
$\mathrm{requires\_human\_review}(s)$ holds.
Escalation $\sigma=\mathrm{escalate}$ maps to $s^{I}$ for institutional disposition.

\paragraph{Governance graph.}
The empirical \texttt{GovernanceGraph} $G=(V,E)$ aggregates simulated traces:
$|V|=3$ macro states, weighted edges $(s,\sigma,s')$ with estimated
$\hat{P}(s' \mid s,\sigma)$ from $N=50$ balanced-profile decisions.
The Graphviz artefact \path{results/governance/formal/formal_governance_graph.dot}
visualises the machine.

\paragraph{Formal audit metrics.}
The \texttt{GovernanceAuditReport} bundles (same values as
$\gamma_{\mathrm{comp}}$ and $\tau_{\mathrm{trace}}$ in
Table~\ref{tab:tsgg-unified-metrics}):
\begin{itemize}[noitemsep]
  \item $\gamma_{\mathrm{comp}}$ (\texttt{governance\_compliance\_score}) $=0.440$
        --- policy-aligned terminal states;
  \item \textbf{institutional\_reliance\_index} $=0.500$
        --- appropriate escalation when required;
  \item \textbf{human\_override\_resilience} $=0.093$
        --- corrective overrides when AI advice is incorrect;
  \item $\tau_{\mathrm{trace}}$ (\texttt{decision\_traceability}) $=1.000$
        --- complete $(s^{AI} \rightarrow s^{H} \rightarrow s^{\cdot})$ audit chains.
\end{itemize}

\paragraph{Positioning.}
This FSM separates \emph{advisory automation} (L4--L5) from \emph{accountable disposition}
(L6), enabling institutions to audit compliance, escalation discipline, and trace completeness
before pilot deployment. Metrics are synthetic; the contribution is the \textbf{explicit
governance state machine} and trace schema, not field outcome claims.
