\subsection{E2 Leakage Audit Methodology}
\label{sec:leakage-analysis}

Independent ground truth (E2) is evaluated with a \textbf{leakage audit framework} that quantifies
coupling among \texttt{world\_dynamics}, \texttt{event\_generator}, and
\texttt{ground\_truth\_rules}. The audit does not replace field validation; it documents
\emph{where} benchmark conclusions may inherit synthetic coupling.

\paragraph{Structural overlap.}
We extract canonical variables (zone density, activity, audio, exit throughput), threshold
predicates, and scenario guards from each component. Table~\ref{tab:leakage-audit} reports:
\textbf{shared\_variables\_ratio} (Jaccard on variable sets),
\textbf{shared\_threshold\_ratio} (bucket alignment plus generator--rules semantic match),
and \textbf{shared\_logic\_ratio} (Jaccard on normalized logic predicates).
The composite \textbf{leakage score} $L_S \in [0,1]$ combines these overlaps (higher indicates
greater shared coupling).

\paragraph{Independence layers.}
\begin{itemize}[noitemsep]
  \item \textbf{Procedural independence} --- AST-confirmed absence of
        \texttt{event\_generator} imports in \texttt{independent\_labeler} (score=
        1.00).
  \item \textbf{Semantic independence} --- $1 - $ mean structural overlap (score=
        0.47).
  \item \textbf{Distributional independence} --- Monte Carlo stability of labels and
        agreement under random threshold perturbations (score=
        0.70).
\end{itemize}

\paragraph{Monte Carlo sensitivity.}
We draw $N_{\mathrm{MC}}=50$ perturbations scaling each GT rule
threshold by $U(0.88, 1.12)$ and measure:
(i)~\emph{ground-truth stability} (label multiset overlap),
(ii)~\emph{event stability} (generator outputs under fixed seed; expected $\approx 1.0$ when
only GT rules move),
(iii)~\emph{agreement drift} (change in event--GT agreement).
Scenario-level results appear in Table~\ref{tab:leakage-mc-by-scenario}.

\paragraph{Dependency graph.}
A Graphviz dependency graph (\texttt{results/leakage\_audit/dependency\_graph.dot}) links
components by shared metrics and threshold alignment edges.

\paragraph{Benchmark disclosure.}
\begin{quote}
\textbf{This benchmark is procedurally independent but not distributionally independent.}
\end{quote}

\input{tables/leakage_audit}
