\section{Trust propagation on TSGG}
\label{sec:trust-propagation}

TSGG is positioned as a \textbf{trust-aware reasoning graph}: every vertex $v$ carries
a trust label $T(v)\in[0,1]$, propagated along the pipeline by stage-specific update
operators rather than a single post-hoc composite score.

\paragraph{Trust labels.}
Let $G=(V,E)$ be the TSGG instance for scenario $\xi$ and seed $\zeta$.
For $v\in V$,
\begin{equation}
  \label{eq:tsgg-trust-node}
  T(v) \in [0,1], \qquad T(v_0) = \pi_0,
\end{equation}
where $\pi_0$ is the \emph{benchmark trust prior} from leakage independence
($\pi_0=0.594$ in the current harness).

\paragraph{Update operators.}
Multiplicative propagation composes parent trust with local confidence $\phi$:
\begin{equation}
  \label{eq:tsgg-trust-compose}
  T(v) = \Psi\bigl(T(\mathrm{pa}(v)),\,\phi(v)\bigr)
  = T(\mathrm{pa}(v))\cdot \phi(v),
\end{equation}
with operators:
$\rho$ \emph{evidence reliability},
$\sigma$ \emph{safety-state confidence},
$\kappa$ \emph{causal confidence},
$\omega$ \emph{recommendation confidence},
$\delta$ \emph{governance confidence}, and
$\alpha$ \emph{audit confidence}.

\paragraph{Path trust.}
For a directed path $\pi=(v_1,\ldots,v_k)$ with composed vertex trust as in
Equation~\eqref{eq:tsgg-trust-compose}, path trust is the terminal label
\begin{equation}
  \label{eq:tsgg-path-trust}
  T(\pi) = T(v_k).
\end{equation}
(Local factors $\phi(v_i)$ satisfy $T(v_i)=T(v_{i-1})\cdot\phi(v_i)$ along $\pi$.)
Recommendation trust is $T(r)=T(\pi_r)$ for the path $\pi_r$ terminating at recommendation
vertex $r$ (mean $\bar{T}_r=0.105$ over the audit sample).

\paragraph{Trust-theoretic metrics.}
\begin{itemize}[noitemsep]
  \item \textbf{trust\_consistency} $=0.522$ --- low dispersion of
        mean stage trust (stable propagation profile);
  \item \textbf{trust\_decay} $=0.971$ --- average relative loss
        $1-T(v_k)/T(v_1)$ along audit paths;
  \item \textbf{trust\_recovery} $=0.017$ --- governance-stage uplift
        when $T(g)>T(r)$ after low recommendation trust.
\end{itemize}
Mean node trust $\bar{T}_V=0.127$;
mean path trust $\bar{T}_\pi=0.060$.

\input{sections/trust_flow_figure}
\input{tables/trust_propagation_metrics}

\paragraph{Relation to $\mathcal{I}_{\mathrm{TSGG}}$.}
The composite index in Equation~\eqref{eq:tsgg-trust} summarises macro families for
reporting; trust propagation supplies a \emph{vertex-level theory} with auditable
$T(v)$ and $T(\pi)$ for institutional review.

\paragraph{Disclaimer.}
Trust propagation on synthetic TSGG traces. Operators define a compositional trust theory; values are feasibility descriptors, not calibrated field probabilities.
