\section{Trusted Safety State Governance Graph (TSGG)}
\label{sec:tsgg}

DUALEXIS contributes a \textbf{single scientific artefact}---the Trusted Safety State
Governance Graph (TSGG)---that unifies semantic safety-state reasoning (SSSG), benchmark
leakage auditing, and formal human--AI governance into one auditable pipeline. Prior
decompositions treated these as independent engineering modules; TSGG positions them as
\emph{stages of one trust-bearing decision trace}.

\paragraph{Pipeline.}
The end-to-end chain is:
\emph{evidence $\rightarrow$ safety state $\rightarrow$ causal transition $\rightarrow$ recommendation $\rightarrow$ governance decision $\rightarrow$ audit trace}.
Figure~\ref{fig:tsgg-framework} summarises the architecture; Section~\ref{sec:tsgg-theory}
states the formal theory (axioms, invariants, propositions); Equations~\eqref{eq:tsgg-pipeline}
and~\eqref{eq:tsgg-trust} provide the operational reporting formulation.

\input{sections/tsgg_figure}
\input{tables/tsgg_unified_metrics}

\begin{equation}
  \label{eq:tsgg-pipeline}
  \Phi_{\mathrm{TSGG}}:
  \; E \xrightarrow{\rho} S \xrightarrow{\kappa} C \xrightarrow{\omega} R
  \xrightarrow{\delta} G \xrightarrow{\alpha} A
\end{equation}
where $E$ is a multiset of privacy-bounded evidence records, $S$ a zone-indexed safety-state
trajectory, $C$ causal transitions with typed factors
$(\texttt{contributes\_to}, \texttt{aggravates}, \texttt{mitigates}, \texttt{triggers})$,
$R$ orchestration recommendations, $G$ macro governance decisions over
$S_{\mathrm{gov}}=\{s^{AI}, s^{H}, s^{I}\}$, and $A$ an append-only audit trace.

\begin{equation}
  \label{eq:tsgg-trust}
  \mathcal{I}_{\mathrm{TSGG}} =
  0.30\,\bar{P}_{\mathrm{st}} +
  0.25\,\Pi_{\mathrm{causal}} +
  0.25\,\bigl(0.5\,\pi_{\mathrm{proc}} + 0.5\,\pi_{\mathrm{dist}}\bigr)(1 - L_S) +
  0.20\,\bar{P}_{\mathrm{gov}}
\end{equation}
with $\bar{P}_{\mathrm{st}}=(P_{\mathrm{prec}}+P_{\mathrm{rec}})/2$,
$\Pi_{\mathrm{causal}}$ causal-path completeness, $L_S\in[0,1]$ the leakage score,
$\pi_{\mathrm{proc}},\pi_{\mathrm{dist}}$ procedural and distributional independence,
and $\bar{P}_{\mathrm{gov}}=(\gamma_{\mathrm{comp}}+\tau_{\mathrm{trace}})/2$.
Synthetic harness evaluation yields
$\mathcal{I}_{\mathrm{TSGG}}=0.667$.


\paragraph{Stage semantics.}
\begin{itemize}[noitemsep]
  \item \textbf{Evidence ($E$).} Privacy-bounded observations ingested from the synthetic
        world and event generator (L1--L3).
  \item \textbf{Safety state ($S$).} Zone-scoped semantic labels
        (\texttt{NORMAL} $\rightarrow$ \texttt{EVACUATION\_CANDIDATE}) with temporal edges.
  \item \textbf{Causal transition ($C$).} Typed causal factors and root-cause attribution
        (CSSG backbone inside TSGG).
  \item \textbf{Recommendation ($R$).} Orchestration advisories with mandatory human review
        for elevated severities.
  \item \textbf{Governance decision ($G$).} Macro-state FSM
        $S_{\mathrm{gov}}=\{s^{AI}, s^{H}, s^{I}\}$ with transition alphabet
        $\Sigma$.
  \item \textbf{Audit trace ($A$).} Append-only $(s,\sigma,s')$ chains for institutional review.
\end{itemize}

\paragraph{Benchmark trust.}
The leakage audit supplies $L_S$ and independence estimates $\pi_{\mathrm{proc}}$,
$\pi_{\mathrm{dist}}$ as \emph{external} trust constraints on the evaluation harness---
not as a separate paper contribution. Low $L_S$ with high independence supports interpreting
state and governance metrics as non-leaking descriptive evidence.

\paragraph{Trust-aware reasoning.}
Vertex-level trust propagation (Section~\ref{sec:trust-propagation}) assigns
$T(v)\in[0,1]$ to every TSGG node with operators
$\rho,\sigma,\kappa,\omega,\delta,\alpha$, yielding path trust $T(\pi)$ and
trust-theoretic metrics (consistency, decay, recovery) beyond the composite
$\mathcal{I}_{\mathrm{TSGG}}$.

\paragraph{Positioning.}
TSGG subsumes SSSG (state graph), CSSG (causal layer), E2 leakage audit, and the formal
governance FSM as a \textbf{trust-aware reasoning graph}. Implementation modules remain in
\texttt{dualexis/sssg}, \texttt{dualexis/cssg}, \texttt{dualexis/leakage\_audit},
\texttt{dualexis/governance}, and \texttt{dualexis/tsgg/trust\_propagation.py}.
TSGG unified framework on synthetic confined-space harness. Integrates semantic state graph, causal attribution, benchmark leakage audit, and formal governance traces. Not a field certification.
